Applied Measure Theory for Probabilistic Modeling

### 2022-05-13 paper/paper.tex
edits

\begin{verbatim}
basemeasure(::Normal{()}) = (1/sqrt2π) * Lebesgue(ℝ)
logdensity_def(::Normal{()} , x) = - x^2 / 2 
insupport(::Normal{()}, x) = true
\end{verbatim}

@@

@@

For a given $x \in X$ with $\mu \ll_x \alpha$, let $\nu_x = \kappa(x)$ have base measure $\beta_x$. Then similarly to the independent product, we have
\[
\frac{\dd(\mu \otimes \nu_x)}{\dd(\alpha \otimes \beta_x)} = \frac{\dd\mu}{\dd\alpha}\ \frac{\dd\nu_x}{\dd\beta_x}\ .
\]
Because the types are always available to help us distinguish this from the independent case, it's safe to use the same notation, \verb|μ ⊗ κ|.

Note that this defines a function
\[
\otimes \colon \cM(X) \times (X \to \cM(Y)) \to \cM(Y)\ .
\]
In functional programming, this (together with some laws) is called a \href{https://en.wikipedia.org/wiki/Monad_(functional_programming)}{\emph{monadic bind}} \cite{ramsey2002stochastic}.

>>>>

\begin{verbatim}
basemeasure(::Normal{()}) = (1/sqrt2π) * Lebesgue(ℝ)

logdensity_def(::Normal{()} , x) = - x^2 / 2

insupport(::Normal{()}, x) = true
\end{verbatim}

@@

\chad{need edits here}

@@

For a given $x \in X$ with $\mu \ll_x \alpha$, let $\nu_x = \kappa(x)$ have base measure $\beta_x$. Then similarly to the independent product, we have
\[
\frac{\dd(\mu \otimes \nu_x)}{\dd(\alpha \otimes \beta_x)} = \frac{\dd\mu}{\dd\alpha}\ \frac{\dd\nu_x}{\dd\beta_x}\ .
\]
